\documentclass[]{deedy-resume-openfont}
\begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Profile
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Sebastian}{Wilczek}{sebastian.wilczek@protonmail.com | +49 151 11658748 \\ Noldeweg 16, 40724 Hilden, Germany \\ Birthday/-place: 13. March 1997, 47259 Duisburg, Germany}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Education
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\raggedright

\runsubsection{University of Amsterdam}\descript{| MSc Security \& Network Engineering}\\ \location{Amsterdam, The Netherlands | September 2019 - July 2020}\\
    
\sectionsep

\runsubsection{Fontys University of Applied Sciences}\descript{| BSc Software Engineering}\\ \location{Venlo, The Netherlands | September 2015 - June 2019}\\
Graduated with Cum Laude (Dutch Grading System)\\

\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Experience
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\runsubsection{Instana, an IBM company}\descript{| Software Engineer}\\ \location{Solingen, Germany | September 2020 – Present}
\begin{tightemize}
	\item Building and maintaining the license, sales, and usage data system of a SaaS and on-premise APM product by aggregating, processing, and exposing data for multi-regional, global installations, for ca. 4500 customers.
	\item Integrating software with various external and internal systems, such as Salesforce, Hubspot, Looker, IBM services, and the core Instana product.
	\item Developing React-based frontend applications, including the environment and customer statistics and the Instana query builder.
\end{tightemize}

\sectionsep\runsubsection{Instana}\descript{| Software Engineering Intern \& Working Student Business Team}\\ \location{Solingen, Germany | February 2019 – August 2019}
\begin{tightemize}
	\item Centralization of a Billing component of a SaaS backend to decrease resource consumption and running costs by uniting 1000+ Kafka streams and improving process throughput.
	\item Using existing Apache Kafka, Docker, and CockroachDB infrastructure to extend and redevelop existing and new Java backend applications, reducing hundreds of running components to one scalable system.
	\item Coordinated requirements gathering from engineering and site reliability teams, combining requirements from various DevOps engineers.
\end{tightemize}

\sectionsep

\runsubsection{codecentric AG}\descript{| Software Engineering Intern \& Working Student Digital Integration}\\ \location{Solingen, Germany | September 2017 – January 2018 \& August 2018 – January 2019}
\begin{tightemize}
	\item Development of a File Sharing Platform, in a project team with three other members, being responsible for a new React Frontend and Java Middleware with PostgreSQL database.
	\item Facilitating sprint meetings and performing requirements engineering with team members and stakeholders.
	\item Maintaining AWS EC2 instances and developing various C\# and Java plugins to be deployed on AWS.
\end{tightemize}

\sectionsep

\runsubsection{Fontys University of Applied Sciences}\descript{| Student Teaching Assistant}\\ \location{Venlo, The Netherlands | September 2016 – January 2016}

\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\raggedright
\begin{tabular}{ l l }
	\descript{Software (Proficient)} & {\location{Java, JavaScript, SQL, NoSQL, AWS, Git, Node.js, HTML, CSS, React, React Native}} \\
	\descript{Software (Familiar)}   & {\location{Python, C\#}}                                   \\
	\descript{Software Development}   & {\location{Scrum, Kanban, Pair Programming, Code Reviews}}                                   \\
	\descript{Languages}   & {\location{German (C2), English (C1)}}                                   \\
\end{tabular}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Projects
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\raggedright
  

\runsubsection{\large{Smartphone app development}}
\descript{| JavaScript, Firebase, React Native, Node.js, Expo}\\
Extensive familiarization with Smartphone app development, development of apps such as Social Networks and Social Media Content Management\\
\sectionsep
  

\runsubsection{\large{CAN Bus Security Evaluation}}
\descript{| C, Arduino, CAN Bus}\\
Evaluation of the security of vehicle CAN buses and proposed integrity schemes, in cooperation with Deloitte\\
\sectionsep


\runsubsection{\large{Firefighting VR Simulation}}
\descript{| Unity, JavaScript, Oculus Rift, 3D scanning and modeling tools}\\
Creation of a VR Simulation of Firefighting within inaccessible environments (Hospitals) by using 3D scanning and modeling techniques and improving interactability\\
\sectionsep

\end{document}